### 2019-12-31 Sections/cryptowars.tex
minor changes to cryptowars - finished!

% Shannon proved that such a locking effect is impossible classically.

Here Alice and Bob share a short secret-key of length $K$, and wish to communicate a message $M$ of length $n-$bits. The secret-key is assumed to be unconditionally secure, and can be established via conventional QKD. First off, they agree upon a set of $K$ Haar-random unitaries (but it is sufficient to consider 2-designs) \index{Haar measure}, $\{\hat{U}_k\}$, associating one with each of the possible $K$ keys. The set of $\{\hat{U}_k\}$ unitaries need not be a secret.

Alice then encodes her message into the state $\ket{j}$. Her encryption operation is to apply $\hat{U}_k$ to this state according to Alice and Bob's shared secret-key.

\begin{align}
\ket{j}_k=\hat{U}_k\ket{j},
\end{align}
which Bob is easily able to decrypt using the inverse unitary,
\begin{align}
\hat{U}_k^\dag\ket{j}_k=\ket{j}.
\end{align}

To characterise the security of the scheme, we first note that in the absence of knowing the key or message, and assuming all $j$ and $k$ are equally likely, Eve observes the mixed state,

\begin{align}\label{eq:ghwoirsfjnk}
 \hat \rho_\text{enc}= \frac{1}{2^n} \sum_{j=1}^{2^n} \ket{j}_A\bra{j} \otimes \frac{1}{K}\sum_{k=1}^K U_k\ket{\psi_j}_E\bra{\psi_j}U_k^\dagger   .
\end{align}

The security can now be quantified in terms of the accessible information
\footnote{The accessible information is the maximum of the mutual information between Alice's input states and measurements performed on the encoded state by Eve.}\index{Accessible information} between this state and the plaintext state, which can be upper-bounded as \cite{lupo2015NJP,lupo2014pra},
% 
% 
\begin{align}
    I_c \leq n + \frac{1}{2^n}\max_{\ket\phi}\sum_{j,k} |\braket{ \phi|j}_k|^2 \log |\braket{ \phi|j}_k|^2.
\end{align}
It was shown that this quantity can be made arbitrarily small with key-size scaling as,
\begin{align}
m=O(\epsilon\log n),
\end{align}
\noindent for an $\epsilon$ that can be made arbitrarily small, given $\log K \sim \log{(1/\epsilon)}$, therefore the key size is exponentially smaller than the length of the message. Thus, we have an encryption scheme that requires very frugal requirements in key-size versus message length. It is further showed that such a scheme can be made robust against noise and loss \cite{lupo2014pra, lupo2015NJP}.

@@

In order to measure Alice's signal states, Bob needs to carry out quadrature measurements, which
are defined with respect to Alice's local oscillator. Since it is difficult to maintain coherence 
between Alice's and Bob's LO, often the Alice sends through the LO through the channel together with the signal states. This leaves open some side-channels which Eve can exploit. For example, she can reduce the error which the trusted parties would expect (e.g. of an intercept and resend attack), if she replaces the signal and LO with squeezed states. Other attacks of the LO include Eve exploiting the wavelength dependence of the beam splitters, shape of the LO pulse, phase noises and the non-linearity photo-detectors.

@@

There are various protocols that fall under the category of QDS. The protocols we describe in this section deal with the notion of signing a classical message using tools from quantum information theory.

@@

Whilst the GC-QDS protocol is intuitive, it is also highly impractical due to the experimental requirements. Firstly, the protocol requires for long-storage quantum memories, since the signature and the verification can be separated by long periods of time -- this requirement is one of the major bottle-necks for building a scalable quantum computer. Secondly, multiple copies of the public key are needed, and each receiving party need to perform the SWAP test, the latter involves more quantum communication and ancillary qubits

@@

Since the development of the GC-QDS protocol, the field has undergone major developments and lifted all the restricting requirements of the protocol.

>>>>

Here Alice and Bob share a short secret-key of length $K$, and wish to communicate a message $M$ of length $n$-bits. The secret-key is assumed to be unconditionally secure, and can be established via conventional QKD. First off, they agree upon a set of $K$ Haar-random unitaries (but it is sufficient to consider 2-designs) \index{Haar measure}, $\{\hat{U}_k\}$, associating one with each of the possible $K$ keys. The set of $\{\hat{U}_k\}$ unitaries need not be a secret.

Alice then encodes her message into the state $\ket{j}$. Her encryption operation is to apply $\hat{U}_k$ to this state according to Alice and Bob's shared secret-key. 
% 
\begin{align}
\ket{j}_k=\hat{U}_k\ket{j},
\end{align}
which Bob is easily able to decrypt using the inverse unitary,
\begin{align}
\hat{U}_k^\dag\ket{j}_k=\ket{j}.
\end{align}

To characterise the security of the scheme, we first note that in the absence of knowing the key or message, and assuming all $j$ and $k$ are equally likely, Eve observes the mixed state,
% 
% 
\begin{align}\label{eq:ghwoirsfjnk}
 \hat \rho_\text{enc}= \frac{1}{2^n} \sum_{j=1}^{2^n} \ket{j}_A\bra{j} \otimes \frac{1}{K}\sum_{k=1}^K U_k\ket{\psi_j}_E\bra{\psi_j}U_k^\dagger   .
\end{align}

The security can now be quantified in terms of the accessible information
\footnote{The accessible information is the maximum of the mutual information between Alice's input states and measurements performed on the encoded state by Eve.}\index{Accessible information} between this state and the plaintext state, which can be upper-bounded as \cite{lupo2015NJP,lupo2014pra},
% 
% 
\begin{align}
    I_c \leq n + \frac{1}{2^n}\max_{\ket\phi}\sum_{j,k} |\braket{ \phi|j}_k|^2 \log |\braket{ \phi|j}_k|^2.
\end{align}
It was shown that this quantity can be made arbitrarily small with key-size scaling as,
\begin{align}
m=O(\epsilon\log n),
\end{align}
\noindent for an $\epsilon$ that can be made arbitrarily small, given $\log K \sim \log{(1/\epsilon)}$, therefore the key size is exponentially smaller than the length of the message. Thus, we have an encryption scheme that requires very frugal requirements in key-size versus message length. It is further showed that such a scheme can be made robust against noise and loss.

@@

In order to measure Alice's signal states, Bob needs to carry out quadrature measurements, which
are defined with respect to Alice's local oscillator. Since it is difficult to maintain coherence 
between Alice's and Bob's local oscillators, often the Alice sends the local oscillators through the channel together with the signal states. This leaves open some side-channels which Eve can exploit. For example, she can reduce the error which the trusted parties would expect (e.g. of an intercept and resend attack), if she replaces the signal and local oscillators with squeezed states. Other attacks of the local oscillators include Eve exploiting the wavelength dependence of the beam splitters, shape of the local oscillators pulse, phase noises and the non-linearity photo-detectors.

@@

There are various protocols that fall under the category of QDS. The protocols we describe in this section deals with the task of signing a classical message using tools from quantum information theory.

@@

Whilst the Gottesman-Chuang QDS protocol is intuitive, it is also highly impractical due to the experimental requirements. Firstly, the protocol requires for long-storage quantum memories, since the signature and the verification can be separated by long periods of time -- this requirement is one of the major bottle-necks for building a scalable quantum computer. Secondly, multiple copies of the public key are needed, and each receiving party need to perform the SWAP test, the latter involves more quantum communication and ancillary qubits

@@

Since the development of the Gottesman-Chuang QDS protocol, the field has undergone major developments and lifted all the restricting requirements of the protocol.
